Many Analystis Project

### 2022-02-02 analysis.Rmd
updated

```{r global_options, echo=FALSE, include = FALSE}
knitr::opts_chunk$set(#
  fig.path="Figs/", 
  message=FALSE, 
  warning=FALSE,
  collapse =TRUE,
  echo=TRUE, 
  #results="hide", 
  fig.width= 16,
  fig.height= 9)

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
# libraries
# libraries and settings
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
library("texreg")
library("kableExtra")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
library("ggdag")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

## degroup variables for within and between analysis
## https://cran.r-project.org/web/packages/parameters/vignettes/demean.html
d1 <-
  cbind(d1,
        demean(d1, select = c("anx", "ch", "bg"), group = "country"))

>>>>

```{r global_options, echo=FALSE, include = FALSE}
knitr::opts_chunk$set(#
  fig.path="Figs/", 
  message=FALSE, 
  warning=FALSE,
  collapse =TRUE,
  echo=TRUE, 
  #results="hide", 
  fig.width= 16,
  fig.height= 9)
```

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
# libraries
# libraries and settings
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
library("texreg")
library("kableExtra")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")n
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
library("ggdag")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

## degroup variables for within and between analysis
## https://cran.r-project.org/web/packages/parameters/vignettes/demean.html
d1 <-
  cbind(d1,
        parameters::demean(d1, select = c("anx", "ch", "bg"), group = "country"))

hist(d1$anx)
```
